Dynamic Topic Modeling for Voice Dialogues

### 2024-05-07 paper/main.tex
update methodology

\chapter{Introduction}

@@

The main objectives of the research work:
\begin{enumerate}
    \item Investigate existing solutions for dynamic text and dialogue topic modelling
    \item The definition of the main stages for DTM for audio dialogues
    \item The identification of suitable training data sets and their collection
    \item An exploration of the possibilities of using large language models for some stages and the selection of models suitable for training in limited resources
    \item The development of the architecture of all stages and their interconnections
    \item Selection of appropriate metrics and measurement of the quality of the approaches used at each stage
    \item Visual evaluation of the pipeline inference on choosen audio samples
\end{enumerate}

@@

The pipeline of dynamic thematic modelling of audio dialogues, which will be considered in this paper, is divided into several main stages. 
These include audio-to-text, dialogue segmentation, topic extraction, and topic evolution. 
The approaches and algorithms used in these stages will be described in detail from a theoretical point of view.

\section{ASR approach}

@@

@@

\subsection{Evaluation Metrics}

@@

@@

We will try several Large Language Models by submitting a dialogue segment as input. The prompt for LLM will look like this:

\begin{lstlisting}
    <|user|> 
    utterance_1
    utterance_2
    ...
    utterance_n. 
    Extract N key words or pharases 
    that describe the given dialog between two peoples, 
    do not use more than 2 wrods 
    <|assistant|>

@@

\subsection{Stage Evaluation}

@@

\begin{table}[htb]
    \begin{center}
        \begin{tabular}{ | c | c | c | c |} 
            \hline
            dataset & train/val/test & Avg Turns & Avg tokens \\ 
            \hline
            SuperDialseg & 6984/1322/1322 & 13 & 239 \\ 
            Tiage &  7939/-/1000 & 14.7  & null \\ 
            Product Meetings (QMSum) & 137 & 535.6 & null \\ 
            Academic Meetings (QMSum) & 59 & 819.0 & null \\ 
            Comemitie Meetings (QMSum) & 36 & 207.7 & null \\
            \hline
        \end{tabular}
    \end{center}
\end{table}

@@

\textbf{Pipeline configuration}

MODEL1 will be used in the ASR for audio datasets. 
At the dialogue clustering stage, BERT-based fine-tuning models will be used. 
For topic extraction, the LlaMA 3 8B and Mistral 7B models will be used, in addition to experiments with a smaller model - phi3.

@@

\chapter{Conclusion}

>>>>

\chapter*{Introduction}

@@

The main objectives of the research work is to create and apply Dynamic Topic Modeling pipeline for audio and text dialogues. 
To solve this problem, you will need to complete the following tasks 
\begin{enumerate}
    \item The identification of suitable datasets for experiments
    \item Investigate open-source solutions for ASR, dialogue clustering, topic extraction and topic evolution.
    \item An exploration of the possibilities of using large language models for some stages and the selection of models suitable for training in limited resources
    \item The development of the architecture of all stages and their interconnections
    \item Selection of appropriate metrics and measurement of the quality of the approaches used at each stage
\end{enumerate}

@@

\section{Automatic Speech Recognition}

@@

\subsection{Speaker-diarization}

@@

\section{Evaluation Metrics}

\subsection{Dialogue segmentation}

@@

\subsection{Topic extraction}

\chapter{Methodology}

\section{Pipeline configuration}

The pipeline of dynamic thematic modelling of audio dialogues, which will be considered in this paper, is divided into several main stages. 
These include ASR, dialogue segmentation, topic extraction and topic evolution.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.7]{img/pipeline.png}
    \caption{DTM pipeline}
\end{figure}

All the models in the pipeline were taken from the \href{https://huggingface.co/}{HuggingFace} hub. 
Tools from \href{https://huggingface.co/docs/transformers/index}{transformers}, which is also part of HuggingFace, 
will be used to create the pipeline.

\section{ASR}

The first optional stage is the Automatic Speech Recognition. 
For audio dialogues, text is extracted from the audio track before segmentation. 
For this stage, open-source:
\begin{itemize}
    \item OpenAI Whisper \\
    Link to model: \href{https://huggingface.co/openai/whisper-large-v3}{whisper-large-v3};
    \item pyannote SpeakerDiarization \\
    Link to model: \href{https://huggingface.co/pyannote/speaker-diarization-3.0}{speaker-diarization-3.0};
\end{itemize}

\section{Dialogue Segmentation}

@@

We will try several Large Language Models:
\begin{itemize}
    \item MetaAI LLaMA3 8b \\
    Link to model: \href{https://huggingface.co/meta-llama/Meta-Llama-3-8B-Instruct}{meta-llama3-8b}
    \item Qwen1.5 7b \\
    Link to model: \href{https://huggingface.co/Qwen/Qwen1.5-7B-Chat}{Qwen1.5 7B}
    \item Mistral 7b \\
    Link to model: \href{https://huggingface.co/mistralai/Mistral-7B-Instruct-v0.1}{Mistral 7B}
\end{itemize}

The prompt for LLM will look like this:

\begin{lstlisting}
    <|user|> 
    utterance_1
    utterance_2
    ...
    utterance_n. 
    Please list of high-level topic words 
    in the following dialogue:
    <|assistant|>

@@

@@

\begin{table}[htb]
    \begin{center}
        \begin{tabular}{ | c | c | c | c |} 
            \hline
            dataset & train/val/test & Avg Turns & Avg tokens \\ 
            \hline
            SuperDialseg & 6984/1322/1322 & 13 & 239 \\ 
            Tiage &  7939/-/1000 & 14.7  & null \\ 
            Product Meetings (QMSum) & 137 & 535.6 & null \\ 
            Academic Meetings (QMSum) & 59 & 819.0 & null \\ 
            Comemitie Meetings (QMSum) & 36 & 207.7 & null \\
            \hline
        \end{tabular}
    \end{center}
    \captionof{table}{Datasets}
\end{table}

@@

@@

\chapter*{Conclusion}
